\section{Conclusion}

\lesson{Probably no unit at your institution ``owns'' exam
  administration: different pieces are owned by different units.}

Delivering exams securely and efficiently is not a simple function of
just the LMS, or just the firewall, or just the computer lab facilities, or just the
scheduling, or just the proctors; it requires coordination among all
these elements.
At most campuses, responsibility for any
one of them usually resides in a specific unit, but
nobody ``owns'' entire-course proctoring as a whole.
Achieving it requires new technical and social cooperation across
campus unit boundaries that are usually non-porous.   All of the
challenges we faced inherit from this challenge in some way.

Our pilot in Fall 2023 consisted of a single course with
230 students consuming about 1,000 student-exam-hours and proctored
largely by TAs and one-off student assistants.
2.5 years later, we have successfully scaled to 24 courses from 16 departments, enrolling over
5,000 undergraduates and accounting for over 45,000
seated exam-hours, proctored by a staff of 29 regular proctors (also student assistants).
These students take exams in one dedicated 30-seat CBTF and a second
shared 30-seat lab; the campus has since committed to opening a
dedicated 80--100 seat CBTF in Fall 2026 in a renovated building, 
and that new CBTF is already fully subscribed, months before opening.
All of this is offered as  a ``common good'' campus service operated
by a comprehensive and
well-managed instructional technology unit, which also
has mature processes for hiring, onboarding, and supervision of
student assistants.
This scale-up has not been without additional challenges, including
getting the attention of the campus to recognize the value of
centrally funding a larger effort;
but it has led
to an assessment-delivery model that is (as others before us have found) 
\emph{far\/} superior to traditional exams in most respects.
No one who has tried CBTF exams
wants to go back, and the CBTF is now generating its own demand.

All of that said, we and the SAC understand each other better today,
and the value of being able to handle over 87\% (in Spring 2026) of
exam-related accommodations within the CBTF framework has been an
enormous benefit.
In our case, the CBTF can handle extra time, reduced distraction,
bathroom breaks during exams, and a few others, and we will soon
accommodate standing desks, adjustable-height desks, and certain kinds
of assistive technology.
(Students whose accommodations \emph{cannot\/} be met by the CBTF must
be handled by either course staff or the SAC proctoring center as
before, but that is a far smaller number of students.)
