
\section{Process and Policy Related Issues}


\subsection{Who Paid For All This?}

\lesson{Find flexible funding: since no one ``owns'' exam administration as a whole, no one
owns funding it either.}

We began with an initial internal ``microgrant'' of \$10,000 from the
Division of Undergraduate Education, based on presentations we had
made to multi-department audiences (e.g.\ Deans and Chairs) about the
benefits of mastery learning and the key role of computer-based
testing in supporting it.  This grant supported some initial work
to convert lower-stakes content to PrairielLearn, such as homeworks
and remote quizzes,
to demonstrate what would be
possible in a CBTF setting.
We made every effort to spread the word about the benefits of mastery
learning, understanding that \emph{different supporters need to hear
different messages.\/}  Faculty are concerned about pedagogy but also
about the workload and quality-of-life of their TAs.  The SAC is
concerned about students getting proper exam accommodations.  Deans,
Chairs, and Vice-whatevers are concerned about how best to deploy
limited academic staff budgets to high-leverage activities, and it's
universally agreed that proctoring isn't one.
We got ourselves invited everywhere we could using every connection we
had: faculty lunches in our
own and colleagues' departments, College-level meetings of Deans and Chairs,
external advisory board meetings, teaching and learning center seminars.
Each time we gave a presentation, we tried to show incremental but
positive results that would resonate with that stakeholder.
Evangelizing everywhere, we believed, would help ensure that when
an opportunity appeared, the potential benefactor would be positively
predisposed.

While we have no counterfactual, we believe the approach worked:
after a few months we attracted additional
seed funding of around \$75,000 from the College of Engineering, in
recognition of the fact that the ``first wave'' of courses to
potentially benefit from the CBTF would be homed there.
Later, on the success of that funding, we won two expansive grants
totaling about \$1.5M (shared with two 
other institutions) covering research and content development related
to mastery learning as well as CBTF operations.

Critically, all of these pools of money had considerable flexibility
in how they were spent, and there was some ``informal'' accounting
within the institution as well.  For example, we did not have to pay
to use the shared lab infrastructure since it was already a ``common
good'' service, and their staff were willing to put in some 
extra effort required to help us run them as part-time CBTF spaces
without specific financial compensation.
Similarly, we were able to borrow some internal human resources in IT for various
aspects of on-site hosting and proctor hiring/supervision,
as well as having explicit support in the research grants for IT staff time and
CBTF-specific cloud resources.

\subsection{Institutional Exam Policies}

\lesson{Consider asking forgiveness, rather than permission, if you
transgress the letter of the law in good faith.}

Many institutions have regulations related to when/where students can
take exams.
At our institution, a course is classified as either having a
``written final exam'' or not, and that designation requires committee
approval to modify.
If the course has a written final,  it is assigned a specific, non-negotiable time and room(s) 
during finals week; would a CBTF final have to  overlap that slot, and
indeed could  \emph{all\/} your students demand to take your final at the
campus-selected time even if they had a choice to take it later?
Does a computer-based exam even count as a ``written final''?  How many
angels can dance on the head of a pin?

The main point is that the CBTF paradigm is so thoroughly foreign
compared to ``traditional'' exam administration that you
probably will have some leeway if you're perceived to break a few
eggs.
We suggest clearing your plan in good faith
with your students, and moving forward.  Fortunately, given our
institution's shared governance, faculty usually have
final discretion over such matters, and they are inclined to listen to
students the vast majority of whom are willing to attest to how much
they appreciated the flexibility of being able to schedule their final exam
time.

Similarly, we had not anticipated that the CBTF would interfere with anyone's
financial models, but the summer offering of our pilot course had previously
been 100\% online and asynchronous, including remote exams;
since converting to CBTF exams (remote exams are now possible only due
to a documented disability exception), we can no longer offer the
summer version as a fully online course.  As instructors, we were more
than happy to pay this price in exchange for higher academic integrity
and much more sane exam administration---an argument that is easy to
win among faculty colleagues, but displeased the Summer Sessions program office
since in-person exams reduced the potential
revenue audience for the course.

\subsection{A Cautionary Tale About Cheating}
\label{sec:cheating}

For the remote PrairieLearn quizzes mentioned in the Background section,
students were required to setup
their equipment at home in a such a way that they were both capturing their
activity as a screencast, and had a separate second camera (such as a
cell phone) recording video of the student taking the exam, with 
the student's face and hands visible. Students had to submit both the
screencast and the live video.

After the Fall~2023 final exam, we found one student who did much more
poorly on the final than their performance on the quizzes would
predict.  After a combination of programmatic and manual forensics, we
were able to determine that the student had had someone else take the
quizzes for them, and submitted screencast video that did not match
the ``live'' video of them taking the quiz, on not one but several
quizzes.  The student was disciplined, but we learned a humbling and
discouraging lesson about the brazenness and length to which some students
would go to cheat.  Since that incident, \emph{all\/} summative
assessments for that course are in-CBTF only except for medical
exemptions, and as of Spring 2026, we have had only one confirmed
attempt at in-CBTF cheating (in another course).  Many of our
colleagues had never fully trusted remote exams in the first place;
the final nail has now been driven into that coffin.


