\section{CBTF Configuration}


\subsection{Software: PrairieLearn}

\lesson{Let PrairieLearn host for you.  
Understand and then minimize the interface with campus IT, to minimize the
overall number of moving parts.  There are a few aspects of operations
that probably only they can handle.}

We initially hosted PrairieLearn ourselves, since it was open source
and we didn't know if we'd need to make changes to integrate with our
campus systems.  In retrospect, this was a mistake.

Our IT staff is highly competent and were very cooperative.  However,
this represented a brand-new set of tools and
workflows for them.  Extra effort such as this must be charged to some account,
and even though we had research funds to pay for this, university IT staff time is typically tightly
budgeted.

We initially thought that our low usage would make it reasonable to
run locally: only one course actually trying to run CBTF-like exams,
during which smooth PrairieLearn operation is mission-critical,
and a few other courses using it for homework and practice, which are
typically not.  But as soon as more courses began doing CBTF quizzes,
the manual scaling of Amazon EC2 (Elastic Compute Cloud) resources to
ensure sufficient capacity quickly became a nuisance, with IT staff
needing a 24-hour heads up before any scale-up period.  PrairieLearn
hosting would have made this transparent.

In addition, the open-source software does not include PrairieTest for
scheduling the CBTF.  Even with only one course to schedule, we
underestimated how useful PrairieTest would be, as we would discover
when we tried to do reservations ourselves.


\subsection{Hardware}

PrairieLearn exams require only a browser; any heavy lifting such as
code autograding is done on the server side by managing Docker
containers (another reason to have PrairieLearn host for you, although
as a caveat, a course requiring custom external grading containers costs more
than 2x per seat as one that doesn't).
The computers in the shared labs are several generations old---some
are nearly 15 years old---and 
were running Windows 10 at the time (recently upgraded to Windows 11,
which required a custom installer since Windows 11 needlessly insists
on more recent model CPUs than what these had).
These were fine for the task, since
PrairieLearn does a good job of adhering to widely-adopted Web
standards for the browser GUI and (importantly) accessibility.
When it came time to outfit a new 30-seat room as a full-time CBTF, we
purchased mini-PCs on Amazon for under \$500 each, including
keyboards, 22'' or 24'' monitors, and mice.
All of these computers have wired Ethernet; we know better than to
rely on wi-fi for something so mission-critical in a densely-occupied room.

The computers are centrally managed.
Our shared labs use a campus-level Active Directory setup that allows
configuring different group policies (profiles) that allow blocking
software installation and filesystem access, locking out most of the
Internet, and so on.
A profile was created for CBTF use that 
disables USB ports (to prevent students bringing USB-borne materials
to an exam) and has virtually no software installed other than a Web
browser and some audio files of white noise for students
who want to block out audio distractions.
We use the open source Clonezilla to uniformly image all machines, and
DeepFreeze software is used to restore the computer to a specific
state whenever an account is signed out. This prevents the saving of
any data (including cookies, files, etc.) on the computer's local filesystem.


\subsection{Networking}
\label{sec:networking}

\lesson{Delivering assessments securely is difficult if the LMS itself isn't
  designed to do so.}

Each lab has its own subnet, so the campus-level firewall was
configured to lock out most of the
Internet when accessed from one of the labs, except for the servers
needed to access PrairieLearn exams. 
One
caveat regarding this configuration was that attempting to access
any blocked site resulted in the same error message one would see if
there were no Internet connection at all.
Some students would make a typo in accessing PrairieLearn or
PrairieTest, see this error, and report to the proctor that their
computer had no Internet.  (This despite the fact that upon signing in
to the CBTF profile, there was an immediate and obvious desktop
shortcut that students were instructed to open to go directly to PrairieTest.)
An alternative would be to use Windows-level firewall facilities
rather than relying on a network firewall.

However, firewalling isn't enough to deliver secure exams.  
Specifically, our requirements for a secure exam are:

\begin{enumerate}

\item The exam can only be accessed while inside one of the CBTF
  spaces.

\item An exam can only be accessed by a particular student during
    the specific time of that student's reservation for that exam.  (That is, a
    student cannot make a reservation for exam A and use the
    opportunity to peek at exam B.)

 \item If the platform serving the exam is also the platform where
    homework assignments and other course materials are located,
      those other materials must not be accessible to the student
      while in the CBTF.

\end{enumerate}


Our campus LMS is Canvas, but even though it supports (impoverished)
``quizzes,'' it is not designed to deliver them securely.
While it supports item 1 by specifying CIDR blocks (IP subnets) to
which exam access is limited, supporting item 2 requires manually
editing each student's allowed exam time window in Canvas.
Furthermore, Canvas provides no way to restrict access to other
materials in the course space from within a particular CIDR
block---the only solution is to completely unpublish all other course
materials temporarily during a multi-day exam window, thereby making
them unavailable to all students during that window.

Some colleagues have reported using lockdown browsers such as
Respondus, but this leads to (at least) two problems, in addition to
the fundamental problem that such a browser is essentially spyware.
First, a lockdown browser must be installed and configured to work
with a particular set of applications (that is, a particular LMS), so
there is an $M\times N$ problem of licensing and installing a browser
to work with each LMS that could be used to administer exams.  Second,
if the LMS itself is not designed for secure delivery, careful
attention must be paid to avoid restricting access to secondary sites
that are actually needed for the exam, such as those that serve images
or provide an embedded coding environment, while blocking sites that
are truly unauthorized.  We judged this
Whac-A-Mole\footnote{Whac-A-Mole is a registered trademark (1975) of
Bob's Space Racers, Inc. Really.} to be unproductive and risky.

The correct solution is therefore a combination of a properly configured IP
firewall and an application that is actually
designed to deliver secure assessments (as defined by the above
requirements).  PrairieLearn is correctly designed for this use case.
The IP firewalling may be either host-level or CIDR-level, but is
independent of the application, unlike lockdown browsers.
At our institution, we created 
a CBTF-specific login profile whose password is publicly known.  That
profile is only available inside CBTF rooms, is configured with  the
necessary firewall rules to block browser access to any web site other
than PrairieLearn and our
campus SSO, and is the only profile from which in-CBTF exams are
accessible at all.


\subsection{Authentication}
\lesson{Two-factor authentication (2FA) can present subtle pitfalls.}

Most software systems integrated at our institution, including PrairieLearn, support
single sign-on (SSO) login via our Shibboleth-based institutional authentication
system.
However, as a matter of campus policy, most
SSO-accessible sites trigger a 2FA flow%
%\footnote{\url{https://calnet.berkeley.edu/calnet-2-step}}
\footnote{\url{URL blinded for review}}
to complete login.
The most common way to do so is to respond to a challenge on one's
cell phone via a particular app (Cisco Duo in our case), but there are
other ways as well.  The 2FA requirement led to
various failure modes:

\begin{itemize}

\item Wifi and/or cellular data coverage is weak in the basement where the labs are, so the phone
  cannot complete the 2FA flow.
\item The student recently obtained a new cell phone and has not yet set
   up the 2FA app and linked it to campus.
\item The student normally uses a different method to complete 2FA,
  such as a physical USB token, tablet, or touchID-capable laptop,
  none of which are permitted in the CBTF.

\end{itemize}

The correct solution for us in our full-time CBTF is to disable 2FA
for logins on the CBTF's CIDR block.  But this is possible only with
close cooperation with campus IT (happily, the team responsible for
2FA and the team responsible for maintaining the shared instructional
labs are in the same campus unit) and because the full-time CBTF's
computers have their own CIDR block.  In one of our still-shared CBTF
spaces where we cannot disable 2FA, we allow students to have their
devices for the first 10 minutes of each exam slot in case needed to
complete login; at the 10-minute mark, before the proctor ``opens''
the exam in PrairieTest, all devices must be placed at the front of
the room.



\subsection{Accessibility}

\lesson{There are more accommodations in heaven and earth
  that are dreamt of in your philosophy.}

Accessibility goes far beyond
the capabilities of the software, which in the case of PrairieLearn
are very good.

Once the pilot was over and we needed to start paying
PrairieLearn to host the software, as a vendor they needed to meet
strict standards of accessibility (a11y).  The good news is their software
does a great job of this, enough to satisfy our very finicky campus review.

However, there are aspects of a11y you must deal with during
a pilot, such as the physical a11y limitations of the room itself: Can
wheelchairs be accommodated?  Standing desks?  Adjustable height
desks?  
  
Try to get your Disabled Students Program (it has different names at
different institutions; we'll generically refer to it as DSP) on board
early.
We found this challenging
because initially they were quite defensive at the concept of a CBTF
serving an entire course, insisting that every seat be accessible, whereas
our goal was to identify which accommodations
can be met straightforwardly, and continue handling the rest by
one-off means.  \emph{Be sure you communicate to your DSP that while you're
hoping to accommodate a subset of students adequately within the
constraints of your CBTF, you will still accommodate all students as
needed, by having others take exams outside your CBTF.}

For example, some students have a ``reduced distraction during exams''
(RD) accommodation.
We were dismayed that we couldn't find any single set of rules
defining the physical parameters of this accommodation in a standard
way within UC Berkeley, let alone systemwide across the nine UC
campuses.
We had
seen photos of UIUC's CBTF in which a subset of RD testing stations
were created facing the wall and flanked by tall cubicle partitions
(to minimize visual distractions) and with noise-cancelling
headphones provided (to minimize auditory distractions).  In the end,
we were able to work with our DSP office to specify a configuration involving headphones and view
partitions that our DSP office agreed would satisfy the RD requirement
for most students, with the caveat that students who had more
stringent needs (e.g. ``must take the exam alone in a room'') would
still be accommodated, just not in the CBTF.

(Our DSP office has a proctoring facility for students needing
accommodations, but it is vastly oversubscribed.  We had been trying
from the start to convey the message that by handling ``common''
accomodations such as reduced distraction and extra time on exams, we
could relieve the DSP proctoring center of much workload.  It has
taken a long time to reach this understanding, but as of February 2026, over
85\% of all exam-related accommodations approved by DSP can be handled
within our CBTF.)

