\section{Physical Configuration}
\label{sec:physical}

\subsection{Computer Lab? Or Open Space? Whose?}
\lesson{If you need to leave shared space the way you found it,
  carefully walk through every aspect of the experience to enumerate
  physical access, virtual access, setup, teardown, and storage needs.}

We were
determined to find labs with centrally-managed hardwired computers, rather than
using student laptops with Wi-Fi in a classroom: the latter is a viable use
case, but a scenario we simply do not trust for high-stakes exams.
Our departmental
computer labs, though underutilized since
most students own laptops, were scheduled in a 
coarse-grained and non-transparent way that made
them hard to ``rent'' as CBTF space.
In contrast, the two instructional labs we were able to schedule part-time
(Figure~\ref{fig:spaces}) were centrally operated, which 
meant there were mature and centralized
procedures for scheduling the rooms, gaining access, and handling IT
and  physical plant maintenance concerns.
The access protocol required the ``tenant''
to borrow a physical key, 
so we had to work out a system by which our rotating staff of proctors could obtain and return 
physical keys before and after each exam shift.
If you're planning on running evening exams, be sure the building
containing the labs is accessible to students after hours.
And if you're planning to fill an empty room with desks and computers,
keep in mind that the room may or may not have sufficient
power,
wired networking, or fire-safety occupancy allowance to serve as a CBTF.

Since we couldn't make permanent changes to the shared-space
facilities, we purchased Velcro-attachable anti-glare/privacy screens for
each workstation\footnote{\url{https://www.amazon.com/dp/B0C9L8NQLW}};
our proctors would  arrive 30 minutes before the
first reservable exam shift to attach them, then stay a bit later to
remove them.
We also bought a few pairs of
noise-cancelling headphones (for Reduced Distraction accommodations,
as Section~\ref{sec:a11y} describes) and various packs of scratch paper color-coded
for different sessions.
(Both ideas were stolen from UIUC.)
A shared CBTF therefore needs a place where such
supplies can be securely stored when others use the space.  

Similarly, we  needed a way for students to keep smart
watches, phones, bags, and so on away from testing workstations.  Our shared
labs didn't have any good place for this, so students placed
their belongings under the desk, where unfortunately it's harder to
spot students fidgeting with them.
Similarly, beware of items in bulky sweater or jacket
pockets when those garments aren't removed.  In
the permanent spaces we later obtained, we installed dedicated racks
for students to leave all personal effects.
A major caveat to ``no personal devices'' is two-factor
authentication (Section~\ref{sec:networking}).


\subsection{Accessibility: Less Standard Than Expected}
\label{sec:a11y}

\lesson{Accommodations definitions and procedures are highly bespoke.
  Understand early
  how responsibility for handling accommodations will
  impact existing workflows.}

PrairieLearn's accessibility compliance is exemplary, as are the physical 
affordances of our shared labs.
But exam accommodations transcend these specific categories,
so we approached our Student Accommodations Center (a generic term for
the campus unit that serves students with disabilities that may impact
their educational experience; SAC hereafter) early, hoping 
for advice and assistance with design elements such as 
Reduced Distraction stations.
Our SAC has a proctoring facility for students with disabilities,
but it is vastly oversubscribed.  
We tried to message that by handling ``common''
accomodations such as reduced distraction and extra time,
which collectively account for more than 80\% of all exam-related
accommodation requests at our institution, we could
could reduce workload on their proctoring center.
However, 
the SAC was initially apprehensive about the idea of a CBTF
serving an entire course, and reluctant to engage with us.
In retrospect, we believe one possible reason was that our whole-class
``one size fits most'' proctoring model was very far away from their
usual operating model, so they may have assumed that we were
trying to either
co-opt their responsibilities or incompetently
scale up what they were already doing.

The second-most-common exam-related accommodation at our institution
is ``reduced distraction (RD) environment.''
We were surprised and dismayed to discover that there was no precise definition
of the physical parameters of this accommodation, and
that practices for handling it seemed to vary
from course to course, the most widely used practice being to
underfill a room to 30--50\% capacity.
For our pilot course's final exam, we
restricted reservations for designated ``underfull'' sessions to students with
an RD accommodation; Section~\ref{sec:reservations} describes why this turned
out to be needlessly painful.
As other courses began using the proto-CBTF after Fall 2023,
our departmental liaison to
the SAC office, who had a close working relationship with them,
engaged them
to develop
a configuration involving headphones and inexpensive view
partitions\footnote{\url{https://www.amazon.com/dp/B0F3CVPDYC}} that
SAC agreed would satisfy the RD requirement for most
students, eliminating the need to underfill the room.
Despite the low cost of these dividers, we configured only a few stations
this way based on historical data,
since dividers make it more
difficult for proctors to spot suspicious behaviors.
The result of these efforts
is that today our scaled-up CBTF handles over 87\%  of
exam-related accommodations, saving hundreds of hours of course staff
time and reducing the proctoring load on our SAC.  Students
whose accommodations cannot be met by the CBTF must
be handled by either course staff or the SAC proctoring center, as
they were before.

A challenge that did not arise with the (inefficient) homegrown
reservations system described in Section~\ref{sec:reservations}, but surfaced when we switched in Spring 2024 to
using PrairieTest and hosted PrairieLearn,
involved our institution's accommodations-handling
workflow.  We have since learned that our workflow is neither better nor worse than
that of other institutions---they are just all bespoke.
PrairieTest has robust accommodation-handling facilities,
%% so that (for
%% example) students with extra-time accommodations receive the extra
%% time automagically, and those with reduced-distraction or
%% assistive-technology accommodations are steered to designated test
%% stations designed to meet those needs.
but it was designed around a workflow in which students
present accommodation letters directly
to CBTF staff, who are uniquely authorized to
% are the only ones who have the ability to
note the
accommodations in PrairieTest.
But at our institution,
accommodation information is provided \emph{only\/} to
the student's instructor, who becomes a (fallible) middleman who must convey it to CBTF
staff.
Yet CBTF staff cannot enter accommodations until
\emph{after\/} the student has signed into PrairieTest at least once---and if the 
student has done so to make their first exam
reservation (not an unusual scenario), \emph{a~fortiori\/} that reservation will not reflect
their accommodations.
% because CBTF staff have been unable to enter them!
This Kafkaesque process caused significant friction for students and
faculty, though PrairieTest's workflows are being made more flexible
in response to such concerns.
